Verifying Demonstrations

### 2018-05-22 paper/properties.tex
Edits beginning of desired properties

On our setting, we have three potential adversaries: Alice, Eve and Mallory.
\seb{I changed the name of Grace to Eve to be consistent with the introduction}
Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Eve, the totalitarian dictator, is to decrease the count but also additionally to deanonymize some of the participants in order to arrest them or convince them to change their minds.
Finally, Mallory represents another nation state and has some interest in affecting the stability of Eve's regime, for Mallory's own 
gain, thus supporting either Eve or Alice as he see fits.
Thus, the objective of Mallory will also be to either increase or decrease the count.
\seb{we have to justify why Mallory is not captured either by Alice or Eve}
In addition, Mallory could also have simply for objective to cause a denial-of-service attack on the architecture of \PRIVO.
In the following two subsections, we will now formally define some security properties specifying the computational effort needed by the adversaries to succeed.

@@

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility:] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability:] every voter can verify that their vote is 
    included in the result.
\end{description}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

To define these properties more formally in the context of protest, we desire three verifiability requirements, among which eligibility can be further broken up in four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that it has not been counted before.
    \begin{requirements}
    \item \emph{Temporal eligibility}:%
      \label{CreatedAfterStart} prove that the proof was created after the start of the protest and
      %\label{CreatedBeforeEnd} prove that the proof was created 
      before the end of the protest.
    \item \emph{Spatial eligibility}
      \label{SpatiallyRelated} prove that the proof is spatially related to the physical location or journey of the protest.
    \item \emph{One-proof-per-person}:%
      \label{CountOnce} prove that no individual can be counted more than once for a particular protest.
    \item \emph{Designated event}:%
      \label{DesignatedEvent} prove that the proof is designated for the protest.
    \end{requirements}

>>>>

In our setting, we have three potential adversaries: Alice, Grace and Mallory.
\seb{I changed the name of Grace to Eve to be consistent with the introduction}
\daniel{Changed back to Grace since that's what's in the intro now.}
Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Grace, the totalitarian dictator, is to decrease the 
count but also additionally to deanonymize some of the participants in order to 
arrest them or forcefully convince them to change their minds.
Finally, Mallory represents another nation state and has some interest in 
affecting the stability of Grace's regime, for Mallory's own gain, thus 
supporting either Grace or Alice as she see fits.
Thus, the objective of Mallory will also be to either increase or decrease the count.
\seb{we have to justify why Mallory is not captured either by Alice or Grace}
In addition, Mallory could also have simply as her objective to cause a 
denial-of-service attack on the architecture of \PRIVO.
In the following two subsections, we will formally define some security 
properties specifying the computational effort needed by the adversaries to 
succeed.

@@

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility:] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability:] every voter can verify that their vote is 
    included in the result.
\end{description}
We translate the votes into \emph{participation proofs}.
Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

To define these properties more formally in the context of protest, we desire three verifiability requirements, among which eligibility can be further broken up in four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each 
    participation proof provides temporal and spatial eligibility and that only 
    one participation proof is counted per individual.
    \begin{requirements}
    \item \emph{Temporal eligibility}:%
      \label{CreatedAfterStart} prove that the proof was created after the start of the protest and
      %\label{CreatedBeforeEnd} prove that the proof was created 
      before the end of the protest.
    \item \emph{Spatial eligibility}
      \label{SpatiallyRelated} prove that the proof is spatially related to the physical location or journey of the protest.
    \item \emph{One-proof-per-person}:%
      \label{CountOnce} prove that no individual can be counted more than once for a particular protest.
    \item \emph{Designated event}:%
      \label{DesignatedEvent} prove that the proof is designated for the protest.
    \end{requirements}
